Hydrodynamics of a Semipermeable Inextensible Membrane Under Flow and Confinement

### 2021-05-19 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
fixed up a few figures
yny

\textcolor{magenta}{
%As was done for the closely-fit channel, we use
%equation~\eqref{eqn:areaROCdecomposed} to investigate the effects of the
%tension and bending forces on semipermeability.
Figure~\ref{fig:contractingRAdecomp} shows the rate of change of the
reduced area due to membrane tension (blue curves), membrane bending (red curves),
and the total membrane force (dashed black curves). Again, the tension is responsible
for the majority of the permeating flux. However, when compared to the
closely-fit channel example, the bending does have more of a
contribution because of the lower maximum imposed velocity. While we
only decompose the membrane force into tension and bending for the two
vesicles that successfully pass through the contraction, we also plot
the total membrane force for the two vesicles that do not pass through
the contraction (dash-dotted green curves). The vesicle does deflate with a smaller
semipermeability coefficient and a smaller maximum imposed velocity, but
the rate of efflux is insufficient for successful passage of the vesicle
through the contraction.}

@@

>>>>

\textcolor{magenta}{
%As was done for the closely-fit channel, we use
%equation~\eqref{eqn:areaROCdecomposed} to investigate the effects of the
%tension and bending forces on semipermeability.
Figure~\ref{fig:contractingRAdecomp} shows the rate of change of the
reduced area due to membrane tension (blue curves), membrane bending (red curves),
and the total membrane force (dashed black curves). Again, the tension is responsible
for the majority of the permeating flux. While we
only decompose the membrane force into tension and bending for the two
vesicles that successfully pass through the contraction, we also plot
the total membrane force for the two vesicles that do not pass through
the contraction (dash-dotted green curves). The vesicle does deflate with a smaller
semipermeability coefficient and a smaller maximum imposed velocity, but
the rate of efflux is insufficient for successful passage of the vesicle
through the contraction.}

@@

\textcolor{magenta}{
%In our model, the permeating flux of viscous solvent is proportional to the normal component of membrane forces.
%which is equal to the jump in hydrodynamic pressure in our simulations with no viscosity contrast
%between interior and exterior fluids. 
For each of the cases in \S~\ref{sec:free_space} and \ref{sec:confinement}, 
we examine the contribution of the permeating flux from membrane tension and membrane bending forces. In free space, we find that both membrane forces contribute comparably in the simulations. As the vesicle hydrodynamics reaches an equilibrium, the two contributions add to zero as the permeating flux integrates to zero rate of change of the reduced area.
Under strong confinement, however, we find the membrane tension to contribute much more to the permeating flux than the membrane bending. For a vesicle going through a closely-fit channel the maximum flow velocity is $U_{max}=1000$ $\mu$m/s is chosen to match the experimental conditions. Such a large flow velocity contributes to large membrane tension, and thus reducing the time scale for change in water content. For a vesicle going through a contracting channel, we used a smaller $U_{max}$ than in the experiments (where the three-dimensional channel contracts in both cross-stream directions) to examine the effect of membrane permeability. We find that, due to the strong confinement, the membrane tension still dominates the membrane bending in contributing to the permeating flux as in the closely-fit channel.
}
